---
title: "Math3021 DB92728-3 VAN HOU HEI"
output: html_notebook
---
  

```{r}
#install("ISLR2")
library (ISLR2)
library(Hmisc) # for corrlation matrix
library(ggplot2) #of cuz we need to plot the graph
Boston
?Boston
```
How many rows are in this data set? How many columns? What
do the rows and columns represent?
```{r}
dim(Boston) #506 column , 13 rows
```
so we have  506 cases(rows) by upper columns we have    
CRIM - per capita crime rate by town    
ZN - proportion of residential land zoned for lots over 25,000 sq.ft.   
INDUS - proportion of non-retail business acres per town.   
CHAS - Charles River dummy variable (1 if tract bounds river; 0 otherwise)    
NOX - nitric oxides concentration (parts per 10 million)    
RM - average number of rooms per dwelling   
AGE - proportion of owner-occupied units built prior to 1940    
DIS - weighted distances to five Boston employment centres    
RAD - index of accessibility to radial highways   
TAX - full-value property-tax rate per $10,000    
PTRATIO - pupil-teacher ratio by town   
B - 1000(Bk - 0.63)^2 where Bk is the proportion of blacks by town    
LSTAT - % lower status of the population    
MEDV - Median value of owner-occupied homes in $1000's    
Make some pairwise scatterplots of the predictors (columns) in
this data set. Describe your findings
```{r}
Boston$chas <- as.numeric(Boston$chas) # we need to convert int to double 
Boston$rad <- as.numeric(Boston$rad)# we need to convert int to double
pairs(Boston) # pairwise scatterplots
```
some of them varabiles are correlated.
by part (b) we look for correlation matrix
```{r}
flattenCorrMatrix <- function(cormat, pmat) {
  ut <- upper.tri(cormat)
  data.frame(
    row = rownames(cormat)[row(cormat)[ut]],
    column = rownames(cormat)[col(cormat)[ut]],
    cor  =(cormat)[ut],
    p = pmat[ut]
    )
}
res2<-rcorr(as.matrix(Boston))
flattenCorrMatrix(res2$r, res2$P)
```
by the result(corrlation coefficient and p-values) abrove we can denote there are corrlation between crime rate with other columns(predictor)
```{r}
lapply(Boston, summary)

```
```{r}
qplot(Boston$crim, binwidth=5, xlab= "Crime rate", ylab= "Number of Suburbs")+ theme_light()
qplot(Boston$tax, binwidth=50, xlab="Full-value property-tax rate per $10,000", ylab="Number of Suburbs")+ theme_light()
qplot(Boston$ptratio, binwidth=5, xlab="Pupil-teacher ratio by town", ylab="Number of Suburbs")   + theme_light()
   
 
```
First graph we denoted that the median and maximum crime rate values are 0.25651 and 88.97620 repectively 
```{r}
for(i in 1:5)
{
   perIndex = i * 10
   selection <- subset(Boston, crim>perIndex )
   rate <- nrow(selection) / nrow(Boston) * 100
   result <- paste(rate, "% neighborhood have crime rate abrove " ,perIndex  , "%", sep=" ")
   print(result)
}
```
since by the tax rate graph we missed the region 4xx ~ 600+
so 
```{r}
 
selection <- subset(Boston, tax<600)
nrow(selection) / nrow(Boston) * 100
selection <- subset(Boston, tax>600)
nrow(selection) / nrow(Boston) * 100

```
How many of the census tracts in this data set bound the Charles
river?
```{r}
ans <-nrow(subset(Boston, chas==1)) # chas is charles river where i is contained
print(paste("num of charles river" , ans))
```
What is the median pupil-teacher ratio among the towns in this
data set?
```{r}
ans <- median(Boston$ptratio)
print(paste("the median is " , ans))
```
Which census tract of Boston has lowest median value of owneroccupied homes? What are the values of the other predictors
for that census tract, and how do those values compare to the
overall ranges for those predictors? Comment on your findings.
```{r}
ans <- Boston[order(Boston$medv),] #order by aes first element must be  lowest 
summary(ans)
ans[1,]
```
There is no residential land zoned for lots exceeding 25,000 sq.ft., which is quite high when compared to the median and average crime rates of all Boston areas. This is true in more than half of Boston's neighborhoods.        
In comparison to most suburbs, the proportion of non-retail business acres per town is relatively high.       

This is not one of the suburbs that surrounds the Charles River.    
The content of nitrogen oxides (parts per 10 million) is one of the highest.    

The average number of rooms per household is one of the lowest in the country.    

Owner-occupied units built before to 1940 have the highest proportion of owners.    

One of the shortest weighted average distances to five Boston job centers.    

The highest accessibility index for radial roads.   

One of the highest full-value property-tax rates per $10,000 in the United States.    
One of the town's highest pupil-to-teacher ratios.

The highest number for 1000(Bk - 0.63)2, where Bk is the percentage of black people in each town.   

One of the population's lowest socioeconomic status (percent).    

In the $1000s, the lowest median value of owner-occupied dwellings.   

In this data set, how many of the census tracts average more
than seven rooms per dwelling? More than eight rooms per
dwelling? Comment on the census tracts that average more than
eight rooms per dwelling.

```{r}
for(i in 6:8)
{
   ans <- (subset(Boston, rm>i))
   noOf<- nrow(ans)
   print(paste("There are ",noOf, " suburbs with more than " , i ," rooms per dwelling." ))
   print(summary(ans))
   

}
```
